A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-21 manuscript.Rmd

<!--
```{r}
set.seed(1235)
runif(1)
set.seed(1235)
runif(1)
```
-->
By wrapping code that uses the internal random number generator (here, the command to create a random number from the uniform distribution, `runif(1)`) with the `future` approach, we guarantee that the random numbers will differ across parallel executions of that code, will achieve a high quality of randomness, but still will be deterministic and thus reproducible:

```{r}
future::value(future::future(runif(1), seed = 1235))
```

>>>>

<!--
```{r}
# reproducible but unsafe in parallel code
set.seed(1235)
runif(1)
set.seed(1235)
runif(1)
```
-->
By wrapping code that uses the internal random number generator (here, the command to create a random number from the uniform distribution, `runif(1)`) with the `future` approach, we guarantee that the random numbers will differ across parallel executions of that code, will achieve a high quality of randomness, but still will be deterministic and thus reproducible:

```{r}
# reproducible and safe in parallel code
future::value(future::future(runif(1), seed = 1235))
```
